Analytic Occultation Light Curves in Reflected Light

### 2020-04-03 tex/ms.tex
better notation

% Shorthand for this paper
\usepackage{xifthen}
\newcommand{\BF}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\BS}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\dd}{\ensuremath{\mathrm{d}}}
\newcommand{\STARRYQUADPOINTS}{100\xspace}
\newcommand{\bkappa}{\BS{\kappa}}
\newcommand{\blambda}{\BS{\lambda}}
\newcommand{\bxi}{\BS{\xi}}
\newcommand{\vmax}{{v_\mathrm{max}}}
\newcommand{\kapint}[1]{%
\sum_{i = 0}^{\frac{N - 1}{2}}
\int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
#1
\dd\varphi
}
\newcommand{\lamint}[1]{%
\sum_{i = 0}^{\frac{N - 1}{2}}
\int\limits_{\frac{1}{2}\lambda_{2i}}^{\frac{1}{2}\lambda_{2i+1}}
#1
\dd\varphi
}
\newcommand{\coshalfkap}[1][]{%
\ifthenelse{%
    \equal{#1}{}
}{
    \cos\left(\frac{\bkappa}{2}\right)
}{
    \cos^{#1}\left(\frac{\bkappa}{2}\right)
}}
\newcommand{\sinhalfkap}[1][]{%
\ifthenelse{%
    \equal{#1}{}
}{
    \sin\left(\frac{\bkappa}{2}\right)
}{
    \sin^{#1}\left(\frac{\bkappa}{2}\right)
}}
\newcommand{\DE}{\Delta \BS{E}(k^2, \bkappa)}
\newcommand{\DF}{\Delta \BS{F}(k^2, \bkappa)}
\newcommand{\sgn}{{\mathrm{sgn}}}
\newcommand{\xhat}{\ensuremath{\mathbf{\hat{x}}}\xspace}
\newcommand{\yhat}{\ensuremath{\mathbf{\hat{y}}}\xspace}
\newcommand{\zhat}{\ensuremath{\mathbf{\hat{z}}}\xspace}
\newcommand{\sT}{\ensuremath{\mathfrak{s}^\top}}
\newcommand{\rT}{\ensuremath{\mathfrak{r}^\top}}
\newcommand{\sTe}{\ensuremath{\BF{s}^\top}}
\newcommand{\rTe}{\ensuremath{\BF{r}^\top}}
%
\newcommand{\bg}{\ensuremath{\tilde{\BF{g}}}}
\newcommand{\bp}{\ensuremath{\tilde{\BF{p}}}}
\newcommand{\by}{\ensuremath{\tilde{\BF{y}}}}

@@

%
\section{The Problem}
\label{sec:the-problem}
%
\textbf{Note:}
This section closely follows the
notation and formalism introduced in \citet{Luger2019}. While we
include all of the relevant equations and definitions in
Appendix~\ref{app:starry}, the reader is strongly encouraged to
review \S2--3 of \citet{Luger2019} before proceeding.

\subsection{Review of the \starry algorithm in emitted light}
\label{sec:starry-review}
%
Without loss of generality, assume the body whose flux we wish to compute
has radius unity and sits at the origin of a right-handed Cartesian coordinate
system with the $x$-axis pointing to the right on the sky, the $y$-axis
pointing up on the sky, and the $z$-axis pointing out of the sky
toward the observer; denote this frame by $\mathcal{F}_0$. In $\mathcal{F}_0$,
the surface (emitted) intensity field of the body is described by the
spherical harmonic coefficient vector $\mathbf{y}$. Following
\citet{Luger2019}, when no occultor is present, we may compute the total
visible flux $f_0$ from this body as
%
\begin{align}
    \label{eq:rTA1Ry}
    f_0 = \rTe \BF{A_1} \BF{R} \BF{y}
    \quad,
\end{align}
%
where, from right to left, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
is a Wigner rotation matrix that rotates $\bvec{y}$ to the sky frame
$\mathcal{F}_\mathrm{sky}$ given the body's inclination $i$, obliquity
$\lambda$, and rotational phase $\vartheta$ (Equation~\ref{eq:R}),
%
$\BF{A_1}$ is the change-of-basis matrix from the spherical harmonic
basis $\by$ to the \emph{polynomial basis} $\bp$ in which the integrals
are computed (Equations~\ref{eq:by}, \ref{eq:bp}, and \ref{eq:A1}),
%
and $\rTe$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bp$
(Equation~\ref{eq:rTe}).
%
If instead an occultor of radius $r_o$ is located at position $(x_o, y_o)$,
we instead compute the visible flux $f$ from
%
\begin{align}
    \label{eq:sTARRy}
    f = \sTe \BF{A} \BF{R}' \BF{R} \BF{y}
    \quad,
\end{align}
%
where, as before, $\BF{R}$ rotates the body from $\mathcal{F}_0$
to $\mathcal{F}_\mathrm{sky}$,
%
$\BF{R}' = \BF{R}'(\omega)$ rotates the body on the plane
of the sky by an angle
$\omega = \mathrm{arctan2}(x_o, y_o)$
into a frame $\mathcal{F}_\mathrm{greens}$ in which the
occultor lies along the $+y$-axis (Equation~\ref{eq:R'}),
%
$\BF{A}$ is the change-of-basis matrix from $\by$
to the \emph{Green's basis} $\bg$ in which the integrals are computed
(Equation~\ref{eq:A}),
%
and $\sTe = \sTe(b_o, r_o)$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bg$
(Equation~\ref{eq:sTe}), with $b_o = \sqrt{x_o^2 + y_o^2}$.
For more details, see Appendix~\ref{app:starry} and \citet{Luger2019}.

@@

point on the surface is proportional to the cosine of the angle $\phi$ between

@@

$\phi \ge \frac{\pi}{2}$ are unilluminated and therefore have radiance of zero.

@@

and the angle by which its semi-major axis is rotated away from the
$+x$-axis \xxx{CHECK ME},
    \label{eq:theta}
    \theta &=
        -\mathrm{arctan2}(x_s, y_s)
         & \qquad \mathcal{F} = \mathcal{F}_\mathrm{term}   \\
        \omega - \mathrm{arctan2}(x_s, y_s)
         & \qquad \mathcal{F} = \mathcal{F}_\mathrm{greens}

@@

    \label{eq:Psi}

@@

hemisphere (see Equation~\ref{eq:Psi}), as the operator $\BF{I}$ weights

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/frames.pdf}
        \oscaption{frames}{%
            How \starry computes the flux from a body in reflected light,
            tracking each of the linear transformations from the input map
            (far right) to the output (far left). The label below each map
            denotes the reference frame, while the label above
            each map denotes the basis in which the map is represented.
            Arrows indicate linear operations and are labeled accordingly.
            The upper branch corresponds to the unocculted case, while the
            lower branch corresponds to the case where an occultor is present.
            See text for details.
            \label{fig:frames}
        }
    \end{centering}
\end{figure}

We may now re-write Equations~(\ref{eq:rTA1Ry}) and (\ref{eq:sTARRy}) to
account for this illumination transformation. The flux outside of occultation
is now given by
%
\begin{align}
    \label{eq:rTIA1RRy}
    f_0 & =
    \mathfrak{r}^\top(b)
    \BF{I}(b, 0, r_s)
    \BF{A_1}
    \BF{R}'(-\theta)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad,
\end{align}
%
and the flux during an occultation by
%
\begin{align}
    \label{eq:sTA2IA1RRy}
    f & =
    \mathfrak{s}^\top(b, \theta, b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta, r_s)
    \BF{A_1}
    \BF{R}'(\omega)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{align}
%
A few notes about these equations are in order.
First, we now apply a rotation matrix $\BF{R}'(-\theta)$
(Equation~\ref{eq:R'}) to the unocculted case,
which rotates the body so the semi-major axis of the terminator is aligned
with the $x$-axis; as will become clear in \S\ref{sec:solution-no-occ} below,
this greatly simplifies the integration step. Note the corresponding change
in $\BF{I}$, which we call with $\theta = 0$.
%
Second, in the derivation of Equation~(\ref{eq:sTA2IA1RRy})
we used the fact that $\BF{A} = \BF{A_2} \BF{A_1}$
(Equation~\ref{eq:A}), where $\BF{A_1}$ transforms from
the spherical harmonic basis $\by$ to the polynomial basis $\bp$, and
$\BF{A_2}$ transforms from $\bp$ to the Green's basis $\bg$.
Finally, note that we replaced the integral vectors
$\rTe$ and $\sTe(b_o, r_o)$
with the vectors
$\mathfrak{r}^\top(b)$ and $\mathfrak{s}^\top(b, \theta, b_o, r_o)$,
respectively.
As we mentioned above, we must modify the integration limits to exclude the
nightside, where the weighting by $\BF{I}$ is unphysical.
The vectors $\mathfrak{r}^\top$ and $\mathfrak{s}^\top$ correspond to these
modified integrals, which we devote the rest of this paper to
computing.

Figure~\ref{fig:frames} summarizes the transformations involved in the two
equations above. Starting on the right with a map vector $\BF{y}$ in
the spherical harmonic basis $\by$, defined in some observer-independent frame
$\mathcal{F}_0$, we first rotate it via $\BF{R}$ to the sky frame
$\mathcal{F}_\mathrm{sky}$, in which orientation the body is viewed by the
observer. If there is no occultation (upper branch of the figure), we then
rotate the map once more via $\BF{R}'$ to the integration frame
$\mathcal{F}_\mathrm{term}$, in which the terminator is parallel to the
$x$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$, apply the
illumination transform $\BF{I}$, and finally dot in the solutions to the
surface integrals $\rT$. If, on the other hand, an occultor is present,
we rotate the map from $\mathcal{F}_\mathrm{sky}$ via $\BF{R}'$ to the frame
$\mathcal{F}_\mathrm{greens}$, in which the occultor lies along the
$+y$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$ and $\BF{I}$
to weight the map by the illumination as above. Finally, we change basis
via $\BF{A_2}$ to the Green's basis, in which we compute and dot the
integrals $\sT$.

@@

$\mathcal{F}_\mathrm{term}$

@@

$x$-axis, with the illumination source at $y \ge 0$.

@@

    \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
    \bp(x, y)
    \ \dd y \ \dd x

@@

    \int_{b\sqrt{1 - x^2}}^{\sqrt{1 - x^2}}
    \bp(x, y)

@@

    \ \dd y \ \dd x

@@

recalling that in frame $\mathcal{F}_\mathrm{term}$, $\theta = 0$ by

@@

    \BF{R}'(-\theta)

@@

Before we discuss how to compute the occultation integrals, we must first
develop a procedure to identify the relevant case given the occultor
position $(x_o, y_o)$ and radius $r_o$ and the terminator semi-minor
axis $b$ and angle $\theta$. Then, once the case is determined, we must
identify the relevant integration boundaries, which depend on the points
of intesection between the limb of the body, the limb of the occultor, and
the terminator. We do so in the following section.

\subsection{Case determination and integration boundaries}
\label{sec:which-case}
%
The key to identifying the case corresponding to a given configuration is
to determine whether or not the limb of the occultor intersects the terminator
of the body, and if so, the points of intersection.
Switching momentarily to the frame $\mathcal{F}_\mathrm{term}$,
the equations defining the
\begin{align}
    y_1(x) & = b \sqrt{1 - x^2}
    \nonumber                                       \\
    y_2(x) & = y'_o \pm \sqrt{r_o^2 - (x - x'_o)^2}
\end{align}
%
where $x'_o = $ and $y'_o = $ are the coordinates of the occultor in
$\mathcal{F}_\mathrm{term}$.

Recall that we perform the integration in frame
$\mathcal{F}_\mathrm{greens}$, in which the occultor lies along the $+y$-axis
at $(0, b_o)$, with $b_o = \sqrt{x_o^2 + y_o^2}$. In this frame, the
semi-major axis of the terminator is at an angle $\theta$ with respect to the
$+x$-axis (Equation~\ref{eq:theta}).

\subsection{Cases 1--4}
\label{sec:cases-1-4}
%
Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
occultor does not intersect with
the terminator of the occulted body, and are therefore fairly
straightforward to solve.
%
Case 1 corresponds to any complete occultation of the body, so the
solution for the flux is trivial:
%
\begin{align}
    \label{eq:sT1}
    f_1 = 0
    \quad.
\end{align}
%
Case 2 involves any occultation in which the occultor blocks \emph{only} the
night side of the body (regardless of whether or not it intersects with the
limb of the body). Since the night side intensity is zero everywhere, this case
is also trivial, as the flux is equal to the flux in the no occultation case
(Equation~\ref{eq:f0}):
%
\begin{align}
    \label{eq:sT2}
    f_2 = f_0
    \quad.
\end{align}
%
Case 3 corresponds to occultations in which the occultor blocks \emph{all} of
the night side of the body and \emph{some} of the day side. In this
configuration, the unocculted part of the disk consists only of dayside.
Since we have no intersections with the terminator to worry about,
we may compute the total flux using the \starry formalism from
\citet{Luger2019}, provided we weight the intensity map by the illumination
field:
%
\begin{proof}{}
    \label{eq:f3}
    f_3 = \sTe(b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta, r_s)
    \BF{A_1}
    \BF{R}'(\omega)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{proof}
%
Finally, case 4 involves any occultation in which the occultor blocks
\emph{only} the day side of the body (regardless of whether or not it
intersects with the limb):
%
\begin{proof}{}
    \label{eq:sT4}
    f_4 = f_3 + \hat{f}_0
    \quad,
\end{proof}
%
where we define
%
\begin{proof}{}
    \label{eq:f0hat}
    \hat{f}_0 & =
    \BS{\rho}^\top(-b, r_s)
    \BF{A_1}
    \BF{R}'(-\theta - \pi)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{proof}

>>>>

% Shorthand for this paper
\usepackage{xifthen}
\newcommand{\BF}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\BS}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\dd}{\ensuremath{\mathrm{d}}}
\newcommand{\STARRYQUADPOINTS}{100\xspace}
\newcommand{\bkappa}{\BS{\kappa}}
\newcommand{\blambda}{\BS{\lambda}}
\newcommand{\bxi}{\BS{\xi}}
\newcommand{\vmax}{{v_\mathrm{max}}}
\newcommand{\kapint}[1]{%
\sum_{i = 0}^{\frac{N - 1}{2}}
\int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
#1
\dd\varphi
}
\newcommand{\lamint}[1]{%
\sum_{i = 0}^{\frac{N - 1}{2}}
\int\limits_{\frac{1}{2}\lambda_{2i}}^{\frac{1}{2}\lambda_{2i+1}}
#1
}
\newcommand{\coshalfkap}[1][]{%
\ifthenelse{%
    \equal{#1}{}
}{
    \cos\left(\frac{\bkappa}{2}\right)
}{
    \cos^{#1}\left(\frac{\bkappa}{2}\right)
}}
\newcommand{\sinhalfkap}[1][]{%
\ifthenelse{%
    \equal{#1}{}
}{
    \sin\left(\frac{\bkappa}{2}\right)
}{
    \sin^{#1}\left(\frac{\bkappa}{2}\right)
}}
\newcommand{\DE}{\Delta \BS{E}(k^2, \bkappa)}
\newcommand{\DF}{\Delta \BS{F}(k^2, \bkappa)}
\newcommand{\sgn}{{\mathrm{sgn}}}
\newcommand{\xhat}{\ensuremath{\mathbf{\hat{x}}}\xspace}
\newcommand{\yhat}{\ensuremath{\mathbf{\hat{y}}}\xspace}
\newcommand{\zhat}{\ensuremath{\mathbf{\hat{z}}}\xspace}
\newcommand{\sT}{\ensuremath{\mathfrak{s}^\top}}
\newcommand{\rT}{\ensuremath{\mathfrak{r}^\top}}
\newcommand{\sTe}{\ensuremath{\BF{s}^\top}}
\newcommand{\rTe}{\ensuremath{\BF{r}^\top}}
%
\newcommand{\bg}{\ensuremath{\tilde{\BF{g}}}}
\newcommand{\bp}{\ensuremath{\tilde{\BF{p}}}}
\newcommand{\by}{\ensuremath{\tilde{\BF{y}}}}

@@

%
\section{The Problem}
\label{sec:the-problem}
%
\textbf{Note:}
This section closely follows the
notation and formalism introduced in \citet{Luger2019}. While we
include all of the relevant equations and definitions in
Appendix~\ref{app:starry}, the reader is encouraged to
review \S2--3 of \citet{Luger2019} before proceeding.

\xxx{Unprimed = sky. Prime = greens. Double prime = term.}
\xxx{Emphasize why we can't just analytically weight the nightside by
    zero and integrate as before.}

\subsection{Review of the \starry algorithm in emitted light}
\label{sec:starry-review}
%
Without loss of generality, assume the body whose flux we wish to compute
has radius unity and sits at the origin of a right-handed Cartesian coordinate
system in some frame $\mathcal{F}_0$. In this frame,
the surface (emitted) intensity field of the body is described by the
spherical harmonic coefficient vector $\mathbf{y}$.
An observer views the body from a large distance in the sky frame
$\mathcal{F}$, in which the $x$-axis points to the right,
the $y$-axis points up, and the $z$-axis points out of the sky
toward the observer. Following \citet{Luger2019}, if
an occultor of radius $r_o$ is located at sky position $(x_o, y_o)$,
we compute the visible flux $f$ from
%
\begin{align}
    \label{eq:sTARRy}
    f = \sTe \BF{A} \BF{R}' \BF{R} \BF{y}
    \quad,
\end{align}
%
where, from right to left, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
is a Wigner rotation matrix that rotates $\bvec{y}$ from $\mathcal{F}_0$
to the sky frame $\mathcal{F}$
given the body's inclination $i$, obliquity
$\lambda$, and rotational phase $\vartheta$ (Equation~\ref{eq:R}),
%
$\BF{R}' = \BF{R}'(x_o, y_o)$ rotates the body on the plane
of the sky into the integration frame $\mathcal{F}'$, in which the
occultor lies along the $+y'$-axis (Equation~\ref{eq:R'}),
%
$\BF{A}$ is the change-of-basis matrix from $\by$
to the \emph{Green's basis} $\bg$ in which the integrals are computed
(Equations~\ref{eq:by}, \ref{eq:bg}, and \ref{eq:A}),
%
and $\sTe = \sTe(b_o, r_o)$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bg$
(Equation~\ref{eq:sTe}), with $b_o = \sqrt{x_o^2 + y_o^2}$.
%
If instead no occultor is present, we compute the total
visible flux $f_0$ from this body as
%
\begin{align}
    \label{eq:rTA1Ry}
    f_0 = \rTe \BF{A_1} \BF{R}'' \BF{R} \BF{y}
    \quad,
\end{align}
%
where, as before, $\BF{R} = \BF{R}(i, \lambda, \vartheta)$
rotates the body from $\mathcal{F}_0$
to the sky frame $\mathcal{F}$,
%
$\BF{R}''$ rotates the body on the plane
of the sky into the integration frame
$\mathcal{F}''$ (Equation~\ref{eq:R''})%
\footnote{%
    In \citet{Luger2019}, $\mathcal{F}'' = \mathcal{F}'$, so
    this rotation is trivial: $\BF{R}''$ is just the identity matrix.
},
%
$\BF{A_1}$ is the change-of-basis matrix from the spherical harmonic
basis $\by$ to the \emph{polynomial basis} $\bp$ in which the integrals
are computed (Equations~\ref{eq:bp} and \ref{eq:A1}),
%
and $\rTe$ is the vector of solutions to the integral over
the projected visible disk of the body for each term in $\bp$
(Equation~\ref{eq:rTe}).
%
For more details, see Appendix~\ref{app:starry} and \citet{Luger2019}.

@@

point on the surface is proportional to the cosine of the angle between

@@

this angle is greater than $\nicefrac{\pi}{2}$ are unilluminated and
therefore have radiance of zero.

@@

and the angle $\theta$ by which its semi-major axis is rotated away from the
$+x$-axis (defined \xxx{below}).

@@

    \label{eq:illum}

@@

hemisphere (see Equation~\ref{eq:illum}), as the operator $\BF{I}$ weights

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/frames.pdf}
        \oscaption{frames}{%
            How \starry computes the flux from a body in reflected light,
            tracking each of the linear transformations from the input map
            (far right) to the output (far left). The label below each map
            denotes the reference frame, while the label above
            each map denotes the basis in which the map is represented.
            Arrows indicate linear operations and are labeled accordingly.
            The upper branch corresponds to the occulted case
            (Equation~\ref{eq:sTA2IA1RRy}), while the
            lower branch corresponds to the case where the body
            is unocculted (Equation~\ref{eq:rTIA1RRy}).
            See text for details.
            \label{fig:frames}
        }
    \end{centering}
\end{figure}

We may now re-write Equations~(\ref{eq:sTARRy}) and (\ref{eq:rTA1Ry}) to
account for this illumination transformation. The flux during an occultation
is now given by
%
\begin{align}
    \label{eq:sTA2IA1RRy}
    f & =
    \mathfrak{s}^\top(b, \theta', b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta', r_s)
    \BF{A_1}
    \BF{R}'(x_o, y_o)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:theta'}
    \theta' = \mathrm{arctan2}(x_o, y_o) - \mathrm{arctan2}(x_s, y_s)
\end{align}
%
is the angle of the terminator in the frame $\mathcal{F}'$.
Note that we made use of the fact that
$\BF{A} = \BF{A_2} \BF{A_1}$
(Equation~\ref{eq:A}), where $\BF{A_1}$ transforms from
the spherical harmonic basis $\by$ to the polynomial basis $\bp$, and
$\BF{A_2}$ transforms from $\bp$ to the Green's basis $\bg$.

Similarly, the flux outside of an occultation is now given by
%
\begin{align}
    \label{eq:rTIA1RRy}
    f_0 & =
    \mathfrak{r}^\top(b)
    \BF{I}(b, \theta'', r_s)
    \BF{A_1}
    \BF{R}''(x_s, y_s)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad,
\end{align}
%
where
%
\begin{align}
    \label{eq:theta''}
    \theta'' = 0
\end{align}
%
is the angle of the terminator in the frame $\mathcal{F}''$, by
construction. The transformation
$\BF{R}'' = \BF{R}''(x_s, y_s)$ (Equation~\ref{eq:R''}) rotates
the body so the semi-major axis of the terminator is aligned
with the $x''$-axis; as will become clear in \S\ref{sec:solution-no-occ} below,
this greatly simplifies the integration step.

Note that in both equations we replaced the integral vectors
$\rTe$ and $\sTe(b_o, r_o)$
with the vectors
$\mathfrak{r}^\top(b)$ and $\mathfrak{s}^\top(b, \theta', b_o, r_o)$,
respectively.
As we mentioned above, we must modify the integration limits to exclude the
nightside, where the weighting by $\BF{I}$ is unphysical.
The vectors $\mathfrak{r}^\top$ and $\mathfrak{s}^\top$ correspond to these
modified integrals, which we devote the rest of this paper to
computing.

Figure~\ref{fig:frames} summarizes the transformations involved in the two
equations above. Starting on the right with a map vector $\BF{y}$ in
the spherical harmonic basis $\by$, defined in some observer-independent frame
$\mathcal{F}_0$, we first rotate it via $\BF{R}$ to the sky frame
$\mathcal{F}$, in which the body is viewed by the
observer. If an occultor is present (upper branch of the figure),
we rotate the map from $\mathcal{F}$ via $\BF{R}'$ to the frame
$\mathcal{F}'$, in which the occultor lies along the
$+y'$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$ and $\BF{I}$
to weight the map by the illumination. Finally, we change basis
via $\BF{A_2}$ to the Green's basis, in which we compute and dot the
integrals $\sT$.
If, on the other hand, there is no occultation (lower branch of the figure),
we instead rotate the map via $\BF{R}''$ to the integration frame
$\mathcal{F}''$, in which the terminator is parallel to the
$x''$-axis. We then apply $\BF{A_1}$ to change basis to $\bp$, apply the
illumination transform $\BF{I}$, and finally dot in the solutions to the
surface integrals $\rT$.

@@

$\mathcal{F}''$

@@

$x''$-axis, with the illumination source at $y'' \ge 0$.

@@

    \int_{b\sqrt{1 - x''^2}}^{\sqrt{1 - x''^2}}
    \bp(x'', y'')
    \ \dd y'' \ \dd x''

@@

    \int_{b\sqrt{1 - x''^2}}^{\sqrt{1 - x''^2}}
    \bp(x'', y'')

@@

    \ \dd y'' \ \dd x''

@@

recalling that in frame $\mathcal{F}''$, $\theta'' = 0$ by

@@

    \BF{R}''(x_s, y_s)

@@

Before we discuss how to compute the occultation integrals, we must first
develop a procedure to identify the relevant case given the occultor
impact parameter $b_o$ and radius $r_o$ and the terminator semi-minor
axis $b$ and angle $\theta'$ in the frame $\mathcal{F}'$.
Then, once the case is determined, we must
identify the relevant integration boundaries, which depend on the points
of intesection between the limb of the body, the limb of the occultor, and
the terminator. We do so in the following section.

\subsection{Case determination and integration boundaries}
\label{sec:which-case}
%
The key to identifying the case corresponding to a given configuration is
to determine whether or not the limb of the occultor intersects the terminator
of the body, and if so, the points of intersection.
While we perform the integration in frame $\mathcal{F}'$, finding the points
of intersection with the terminator is easier if we temporarily switch to
the frame $\mathcal{F}''$ (via Equation~\ref{eq:R''}) in which the terminator
is parallel to the $x''$-axis.
In this frame, the equations defining the terminator and the limb of the
occultor are, respectively,
%
\begin{proof}{}
    y''_1(x'') & = b \sqrt{1 - x''^2}
    \nonumber                                               \\
    y''_2(x'') & = y''_o \pm \sqrt{r_o^2 - (x'' - x''_o)^2}
\end{proof}
%
where
%
\begin{proof}{}
    x''_o = b_o\sin\theta'
    \nonumber \\
    y''_o = b_o\cos\theta'
\end{proof}
%
are the coordinates of the occultor in $\mathcal{F}''$.
%
We wish to find the set of $N$ points
$\{{x''}_n~\big|~0~\le~n~<~N\}$
for which
$y''_1(x_n'') - y''_2(x_n'') = 0$. Following \citet{Luger2017}, we may
express this condition as the quartic equation
%
\begin{proof}{}
    \label{eq:quartic}
    A {x''}^4 + B {x''}^3 + C {x''}^2 + D {x''} + E = 0
\end{proof}
%
with coefficients
%
\begin{proof}{}
    \label{eq:quartic-coeffs}
    A &= (1 - b^2)^2
    \nonumber \\
    B &= -4 x''_o (1 - b^2)
    \nonumber \\
    C &= -2 \bigg(
    b^4
    + r_o^2
    - 3 {x''_o}^2
    - {y''_o}^2
    - b^2 \big(1 + r_o^2 - {x''_o}^2 + {y''_o}^2\big)
    \bigg)
    \nonumber \\
    D &= -4 x''_o (b^2 - r_o^2 + {x''_o}^2 + {y''_o}^2)
    \nonumber \\
    E &=
    b^4
    - 2 b^2 \big(r_o^2 - {x''_o}^2 + {y''_o}^2\big)
    + \big(r_o^2 - {x''_o}^2 - {y''_o}^2\big)^2
    \quad.
\end{proof}
%
Although closed-form solutions to quartic equations exist
\citep[see, e.g.,][who solve for the area of overlap between two ellipses
    analytically]{Hughes2011}, they are prone to significant numerical
instabilities. Instead, we solve for the roots of the quartic
numerically by casting it
as an eigenvalue problem \citep[e.g.,][]{Edelman1995} and polish the
results with a few iterations of Newton's method. We find that this is
reasonably computationally efficient and
yields roots with precision within a couple orders of magnitude of machine
epsilon (see \S\ref{sec:performance}).

In general, the quartic defined by Equation~(\ref{eq:quartic}) has
$N=4$ (potentially degenerate) roots, some of which may be complex, and some
of which correspond to intersections with the wrong half of the
terminator ellipse (i.e., the section of the terminator on the far side
of the body). After excluding the unphysical solutions, we are still left with
anywhere between zero and four roots.

\xxx{More here...}

\subsection{Cases 1--4}
\label{sec:cases-1-4}
%
\xxx{This section needs to be revised.}
Cases 1--4 (see Figure~\ref{fig:cases}) involve configurations in which the
occultor does not intersect with
the terminator of the occulted body, and are therefore fairly
straightforward to solve.
%
Case 1 corresponds to any complete occultation of the body, so the
solution for the flux is trivial:
%
\begin{align}
    \label{eq:sT1}
    f_1 = 0
    \quad.
\end{align}
%
Case 2 involves any occultation in which the occultor blocks \emph{only} the
night side of the body (regardless of whether or not it intersects with the
limb of the body). Since the night side intensity is zero everywhere, this case
is also trivial, as the flux is equal to the flux in the no occultation case
(Equation~\ref{eq:f0}):
%
\begin{align}
    \label{eq:sT2}
    f_2 = f_0
    \quad.
\end{align}
%
Case 3 corresponds to occultations in which the occultor blocks \emph{all} of
the night side of the body and \emph{some} of the day side. In this
configuration, the unocculted part of the disk consists only of dayside.
Since we have no intersections with the terminator to worry about,
we may compute the total flux using the \starry formalism from
\citet{Luger2019}, provided we weight the intensity map by the illumination
field:
%
\begin{proof}{}
    \label{eq:f3}
    f_3 = \sTe(b_o, r_o)
    \BF{A_2}
    \BF{I}(b, \theta, r_s)
    \BF{A_1}
    \BF{R}'(\omega)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{proof}
%
Finally, case 4 involves any occultation in which the occultor blocks
\emph{only} the day side of the body (regardless of whether or not it
intersects with the limb):
%
\begin{proof}{}
    \label{eq:sT4}
    f_4 = f_3 + \hat{f}_0
    \quad,
\end{proof}
%
where we define
%
\begin{proof}{}
    \label{eq:f0hat}
    \hat{f}_0 & =
    \BS{\rho}^\top(-b, r_s)
    \BF{A_1}
    \BF{R}'(-\theta - \pi)
    \BF{R}(i, \lambda, \vartheta)
    \BF{y}
    \quad.
\end{proof}
